---
output:
  word_document: default
  html_document: default
---
# Module 2 Assignment 2

## Wilds, Charles

### Introduction to R Markdown

This is my first R Markdown document. It will discuss some of the previous topics in this course. These topics will include atomic vectors, data frames and data types.

This markdown document will review the sales over the past 6 months by constructing a basic plot.

```{r Plot of Sales by Month}
library(tidyverse)
sales <- c(50, 150, 200, 100, 300, 250)
sales

month <- c(1,2,3,4,5,6)
month

qplot(month,sales)
```
Month 5 had the highest sales amount which was 300.

```{r Working with Data Frames}
Yearly_Sales <- data.frame(month=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"),
                           sales=c(150.25, 258.54, 268.55, 122.52,
                                   987, 458.82, 667.23, 845.54, 586.78, 888.58, 756.12, 456.84))
qplot(Yearly_Sales$sales,Yearly_Sales$month)
```
May was our highest sales month and April was our lowest.
