---
output:
  word_document: default
  html_document: default
---
# Module 3 - Assignment 3
## Wilds, Charles
### More Practice with Plots

```{r}
library(tidyverse)
GOOG <- read_csv("GOOG.csv", col_types = cols(Date = col_date(format = "%Y-%m-%d")))
```

#### Google Stock Price Plots

The following is an analysis of Google’s stock price from October of 2019 to October of 2020. This will
include a scatter, line, bar, histogram and boxplot. All the plots represent the closing price on the dates listed on the x-axis.

```{r}

ggplot(data=GOOG, aes(x=Date,y=Close)) +
  geom_point()

ggplot(data=GOOG) +
  geom_line(mapping=aes(x=Date, y=Close))

ggplot(data=GOOG) +
  geom_col(mapping=aes(x=Date, y=Close))

ggplot(data=GOOG) +
  geom_histogram(mapping=aes(x=Close))

ggplot(data=GOOG) +
  geom_boxplot(mapping=aes(x=Close))

ggplot(data=GOOG, aes(x = Date, y = Close)) +
  geom_line() +
  geom_point()

```

You have created many different plots of the same data but some are more helpful than others. Based on
the plots you created, which one do you find most useful and why?
I feel the first line graph we plotted (without the points) is the most helpful. The line gives a great illustration of the increase and decrease in the Y variable, and I feel the points do not help much with this number of observations. If you are trying to find trends, the first line graph is the most helpful. 
#### Google Stock Daily Price Comparisons

```{r Advanced Plots}
ggplot(GOOG) +
  geom_line(aes(x=Date, y= High, color= "High")) +
  geom_line(aes(x=Date, y= Low, color= "Low"))

ggplot(GOOG) +
  geom_line(aes(x=Date, y= Open, color= "Open")) +
  geom_line(aes(x=Date, y= Close, color= "Close"))

ggplot(GOOG, aes(x=Date, y=Close)) +
  geom_area(color="black", fill="blue", alpha=.2)

ggplot(GOOG, aes(x=Date, y=Close)) +
  geom_area(color="blue", fill="green", alpha=.1)

MAYPRICE <- subset(GOOG, Date > "2020-04-30" & Date < "2020-06-01")

ggplot(MAYPRICE, aes(x=Date,y=Close)) +
  geom_point() +
  geom_text(aes(label= round(Close)), size=3, vjust=-1)

APRILPRICE <- subset(GOOG, Date > "2020-03-31" & Date < "2020-05-01")

ggplot(APRILPRICE, aes(x=Date,y=Close)) +
  geom_point() +
  geom_text(aes(label= round(Close)), size=2, vjust=1)
  
```

