---
output:
  word_document: default
  html_document: default
---
# Module 4 Assignment 1
## Wilds, Charles
### Data Transformation

```{r}
library(tidyverse)
state_income <- read_csv("state_income.csv")
```

#### State Incomes

In this markdown file we will first be creating a subset of data from the *state_income* file. We will be using the following variables:
1.) State_Name
2.) State_ab
3.) County
4.) City
5.) Type
6.) ALand
7.) Mean
8.) Median
9.) Stdev

```{r}
state_income2 <- select(state_income, State_Name, State_ab, County, City, Type, ALand, Mean, Median, Stdev)
state_income2 <- select(state_income2, State_ab, everything())
head(state_income2,n=10)
```
```{r}
state_income2 <- rename(state_income2, SquareArea = ALand)
state_income2 <- rename(state_income2, IncomeMean = Mean)
state_income2 <- rename(state_income2, IncomeMedian = Median)
state_income2 <- rename(state_income2, IncomeStDev = Stdev)

head(state_income2,n=10)
```
```{r}
NC_income <- filter(state_income2, State_Name== "North Carolina")
head(NC_income,n=10)
```

#### NC Incomes

We will now use the NC_Income data set to create a summary of the incomes withing North Carolina using the county, city, and type variables.

```{r}
NC_income <- arrange(NC_income, County)
head(NC_income, n=10)
```

```{r}
summary1 <- group_by(NC_income,County)
summary1 <- summarise (summary1, mean= mean(IncomeMean))

summary2 <- NC_income %>%
 group_by(City) %>%
 summarise (mean = mean(IncomeMean))
```
The first new data set summarizes the IncomeMean average and groups the NC_income data set by County and City. The second data set accomplishes all of this in one command.

#### Income Visualization

```{r}
ggplot(data=summary1, aes(x=County,y=mean)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90,vjust =0.5, hjust=1)) +
  labs(y = "Income")


```
Wake County has the highest income. Stokes County has the lowest income. Surry County has the second lowest income.

```{r}
AvgStateIncome <- group_by(state_income2, State_ab)
AvgStateIncome <- summarise (AvgStateIncome, mean= mean(IncomeMean))

AvgStateIncome <- filter(AvgStateIncome, grepl("N",State_ab))

ggplot(data=AvgStateIncome, aes(x=State_ab,y=mean)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90,vjust =0.5, hjust=1)) +
  labs(title = "Mean Income by State",
       x = "State",
       y = "Mean Income")

```

The above scatter plot shows that New Jersey had the highest income and Tennessee had the lowest.
