---
output:
  word_document: default
  html_document: default
---
# Module 5 - Assignment 1
## Wilds, Charles
### Data Wrangling

```{r}
library(tidyverse)
library(readxl)
UN_migrant <- read_excel("UN_migrant.xlsx", 
    sheet = "Table 6", col_types = c("numeric", 
        "text", "text", "numeric", "text", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "text", "text", "text", "text", "numeric", 
        "numeric", "text", "text", "text", 
        "text", "text"), skip = 15)
```

### Part 2 – Cleaning Data with dplyr

```{r}
UN_migrant <- rename(UN_migrant, Country = ...2)
UN_migrant <- rename(UN_migrant, Country_Code = ...4)
UN_migrant <- rename(UN_migrant, Type = ...5)
UN_migrant <- rename(UN_migrant, "1990" = "1990...6")
UN_migrant <- rename(UN_migrant, "1995" = "1995...7")
UN_migrant <- rename(UN_migrant, "2000" = "2000...8")
UN_migrant <- rename(UN_migrant, "2005" = "2005...9")
UN_migrant <- rename(UN_migrant, "2010" = "2010...10")
UN_migrant <- rename(UN_migrant, "2015" = "2015...11")
```

```{r}
Migration <- select(UN_migrant, Country, Country_Code, Type, "1990", "1995", "2000", "2005", "2010", "2015")
```

### Part 3 – Creating tidy data using tidyr

```{r}
Migration2 = pivot_longer(Migration,c('1990','1995','2000','2005','2010','2015'),names_to = 'Year',values_to = 'Cases')
head(Migration2,n=6)
```

```{r}
Migration2$Year <- as.integer(Migration2$Year)
head(Migration2,n=6)
```

### Part 4 – Research Questions

```{r}
library(readr)

RegionalMigration <- select(Migration2, Country, Country_Code, Type, Year, Cases)
RegionalMigration <- filter(RegionalMigration,Country %in% c("Africa","Asia","Europe","Oceania","Northern America","South America"))

Americas <- select(Migration2, Country, Country_Code, Type, Year, Cases)
Americas <- filter(Americas,Country %in% c("Central America","South America","Northern America"))
```

### Worldwide Migration based on Regions

a. Which region in the world had the highest number of migrants in the year 2005? 
Asia
b. Over the years, which region consistently has the most migrants every 5 year span? 
Asia  
Which has the second most?  
Africa
c. What region has seen the fewest migrants over the years?
Oceania
d. Which plot was most useful in answering these questions and why?
The first graph was the most useful because you could see a clear difference in the points on the graph. Both graphs  were a little tight towards the lower totals but the first graph was still more helpful.

```{r}
ggplot(data=RegionalMigration, aes(x=Year,y=Cases, color=Country)) +
  geom_point() +
  labs(y="Migrants", x="Year", title="Worldwide Migration")

```

```{r}

ggplot(data=RegionalMigration, aes(x=Year,y=Cases, fill=Country)) +
  geom_col() +
  labs(y="Migrants", x="Year", title="Worldwide Migration")
```

###  Americas Migration by Region

a. In 1990, which region had the largest number of migrants for the Americas?
Central America
b. Has this region continued to grow since 1990?
No
c. What trends do you notice happening in the Americas over the years?
Central America and Northern America have gone down, South America has had a slight increase starting in 2010
d. Specifically, has Northern America increased or decreased over the years?
Decreased
e. Which plot was most useful in answering these questions and why?
Plot 1 for the same reasons as the previous group of questions

```{r}
ggplot(data=Americas, aes(x=Year,y=Cases, color=Country)) +
  geom_point() +
  labs(y="Migrants", x="Year", title="Americas Migration")
```

```{r}
ggplot(data=Americas, aes(x=Year,y=Cases, fill=Country)) +
  geom_col() +
  labs(y="Migrants", x="Year", title="Americas Migration")
```

