---
output:
  word_document: default
  html_document: default
---
# Module 6 - Assignment 1
## Wilds, Charles
### Lubridate

```{r}
library(tidyverse)
library(lubridate)
library(readr)
Appointments <- read_csv("Appointments.csv")

```

### Working with Dates

```{r}
library( dplyr)

Appointments = mutate(Appointments, ReservationYear="2019")

Appointments = mutate(Appointments, ReservationDate = make_date(month=ReservationMonth, day=ReservationDay, year=ReservationYear))

Appointments = mutate(Appointments, CreationDate = make_date(month=CreationMonth, day=CreationDay, year=CreationYear))

Appointments = mutate(Appointments, ReservationSpan = as.period(interval(CreationDate, ReservationDate)))
```

### Exploratory Analysis

```{r}
summary(Appointments)

```
a. What is the average time between appointment creation and the actual reservation date?
38d 18H 42M 27.6524977944791S
b. What was the max time?
207d 15H 0M 0S
c. What was the min time?
1d 0H 0M 0S

```{r}
Appointments = mutate(Appointments, ReservationSpan = as.numeric(interval(CreationDate, ReservationDate)))

cor(Appointments$ReservationSpan, Appointments$Show, method = "pearson", use = "complete.obs")
```

a. Are ReservationSpan and Show highly correlated?
No

```{r}
ggplot(Appointments, aes(Show)) +
  geom_bar()
```

a. Based on 0 being “no show” and 1 being “show”, did most people make their appointments?
Yes
