---
output:
  word_document: default
  html_document: default
---
# MIS503 – Final Project
## Wilds, Charles
### Zillow Home Value Index Analysis

```{r}
library(tidyverse)
library(dplyr)
library(readr)

Sales <- read_csv("SingleFamilyResidenceSales.csv")
Rental <- read_csv("SingleFamilyResidenceRental.csv")
```

###  Wake County Home Sales

```{r}
WakeCountySales <- filter(Sales, State== "NC" & CountyName == "Wake County")
WakeCountySales <- select(WakeCountySales, RegionName, State, CountyName, Metro, "1996-05", "1997-05", "1998-05", "1999-05", "2000-05", "2001-05", "2002-05", "2003-05", "2004-05", "2005-05", "2006-05", "2007-05", "2008-05", "2009-05", "2010-05", "2011-05", "2012-05", "2013-05", "2014-05", "2015-05", "2016-05", "2017-05", "2018-05")

WakeCountySales <- rename(WakeCountySales, "1996" = "1996-05")
WakeCountySales <- rename(WakeCountySales, "1997" = "1997-05")
WakeCountySales <- rename(WakeCountySales, "1998" = "1998-05")
WakeCountySales <- rename(WakeCountySales, "1999" = "1999-05")
WakeCountySales <- rename(WakeCountySales, "2000" = "2000-05")
WakeCountySales <- rename(WakeCountySales, "2001" = "2001-05")
WakeCountySales <- rename(WakeCountySales, "2002" = "2002-05")
WakeCountySales <- rename(WakeCountySales, "2003" = "2003-05")
WakeCountySales <- rename(WakeCountySales, "2004" = "2004-05")
WakeCountySales <- rename(WakeCountySales, "2005" = "2005-05")
WakeCountySales <- rename(WakeCountySales, "2006" = "2006-05")
WakeCountySales <- rename(WakeCountySales, "2007" = "2007-05")
WakeCountySales <- rename(WakeCountySales, "2008" = "2008-05")
WakeCountySales <- rename(WakeCountySales, "2009" = "2009-05")
WakeCountySales <- rename(WakeCountySales, "2010" = "2010-05")
WakeCountySales <- rename(WakeCountySales, "2011" = "2011-05")
WakeCountySales <- rename(WakeCountySales, "2012" = "2012-05")
WakeCountySales <- rename(WakeCountySales, "2013" = "2013-05")
WakeCountySales <- rename(WakeCountySales, "2014" = "2014-05")
WakeCountySales <- rename(WakeCountySales, "2015" = "2015-05")
WakeCountySales <- rename(WakeCountySales, "2016" = "2016-05")
WakeCountySales <- rename(WakeCountySales, "2017" = "2017-05")
WakeCountySales <- rename(WakeCountySales, "2018" = "2018-05")

WakeCountySales <- pivot_longer(WakeCountySales,c("1996", "1997", "1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018"),names_to = 'YR',values_to = 'ZHVI')

ggplot(data=WakeCountySales, aes(x=YR,y=ZHVI, color= RegionName)) +
  geom_point()+
  labs(y="Home Value", x="Year", title="Wake County Sales")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  scale_y_continuous(name="Home Values (in $)", labels = scales::comma)

ggplot(data=WakeCountySales, aes(x=YR,y=ZHVI, color= RegionName)) +
  geom_col()+
  labs(y="Home Value", x="Year", title="Wake County Sales")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  scale_y_continuous(name="Home Values (in $)", labels = scales::comma)
```

a. What have been the overall trends in Wake County Home Values?

The homes have saw a slight increase from 1999-2008, a slight decrease from 2008-2012, and a rapid increase from 2012-2018. The economic recession in 2008 could be a valid reason for these trends.

b. There were dips in home values in the past 20 years. What years did these occur?

1996-199 and 2008-2012

c. Based on the analysis, where would be the least expensive area to purchase home?

Zebulon

   Most expensive area?
   
Over the course of the 20 years, Cary was continuously the most expensive, but for the most recent year New Hill was the highest.

d. Are any area home values trending down?

The final 7 years of the graph show that there are not any areas currently trending down.

   Is there one area that stands out compared to others?
   
Cary was the highest for the overwhelming majority of the years.

### NC Rental Market

```{r}
Rentals <- filter(Rental, State== "NC" & RegionName %in% c("Asheville","Charlotte","Durham","Fayetteville","Raleigh","Wilmington"))

Rentals <- select(Rentals, RegionName, State, "2010-11", "2011-11", "2012-11", "2013-11", "2014-11", "2015-11", "2016-11", "2017-11", "2018-10")

Rentals <- rename(Rentals, "2010" = "2010-11")
Rentals <- rename(Rentals, "2011" = "2011-11")
Rentals <- rename(Rentals, "2012" = "2012-11")
Rentals <- rename(Rentals, "2013" = "2013-11")
Rentals <- rename(Rentals, "2014" = "2014-11")
Rentals <- rename(Rentals, "2015" = "2015-11")
Rentals <- rename(Rentals, "2016" = "2016-11")
Rentals <- rename(Rentals, "2017" = "2017-11")
Rentals <- rename(Rentals, "2018" = "2018-10")
Rentals <- rename(Rentals, City = RegionName)

Rentals <- pivot_longer(Rentals,c("2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018"),names_to = 'YR',values_to = 'ZHVI')

ggplot(data=Rentals, aes(x=YR,y=ZHVI, color= City)) +
  geom_point()+
  labs(y="Home Value", x="Year", title="North Carolina Rental Market")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  scale_y_continuous(name="Home Values (in $)", labels = scales::comma)

ggplot(data=Rentals, aes(x=YR,y=ZHVI, color= City)) +
  geom_col()+
  labs(y="Home Value", x="Year", title="North Carolina Rental Market")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5))+
  scale_y_continuous(name="Home Values (in $)", labels = scales::comma)

```

a. What has been the overall trend in the rental market around the state? Are there any cities that
have not followed this trend?

The overall trend has been a consistent slight increase in home value over time. Fayetteville, however, has not followed this trend having been well below all the the other cities. Fayetteville is an apparent outlier.

b. Where is the most expensive city to rent in?

Over the full graph, Raleigh has consistently been the most expensive, however, Asheville has been the highest over the 3 most recent years.

   Least expensive?
   
Fayetteville

c. You are trying decide between Wilmington and Asheville. Which market has the lowest rent?
Wilmington

###  Home Values in Select Rental Markets

```{r}
NCHomeSales <- filter(Sales, State== "NC" & Metro %in% c("Asheville", "Charlotte-Concord-Gastonia", "Raleigh", "Wilmington"))

NCHomeSales <- select(NCHomeSales, RegionName, State, Metro, "1996-05", "1997-05", "1998-05", "1999-05", "2000-05", "2001-05", "2002-05", "2003-05", "2004-05", "2005-05", "2006-05", "2007-05", "2008-05", "2009-05", "2010-05", "2011-05", "2012-05", "2013-05", "2014-05", "2015-05", "2016-05", "2017-05", "2018-05")

NCHomeSales <- rename(NCHomeSales, "1996" = "1996-05")
NCHomeSales <- rename(NCHomeSales, "1997" = "1997-05")
NCHomeSales <- rename(NCHomeSales, "1998" = "1998-05")
NCHomeSales <- rename(NCHomeSales, "1999" = "1999-05")
NCHomeSales <- rename(NCHomeSales, "2000" = "2000-05")
NCHomeSales <- rename(NCHomeSales, "2001" = "2001-05")
NCHomeSales <- rename(NCHomeSales, "2002" = "2002-05")
NCHomeSales <- rename(NCHomeSales, "2003" = "2003-05")
NCHomeSales <- rename(NCHomeSales, "2004" = "2004-05")
NCHomeSales <- rename(NCHomeSales, "2005" = "2005-05")
NCHomeSales <- rename(NCHomeSales, "2006" = "2006-05")
NCHomeSales <- rename(NCHomeSales, "2007" = "2007-05")
NCHomeSales <- rename(NCHomeSales, "2008" = "2008-05")
NCHomeSales <- rename(NCHomeSales, "2009" = "2009-05")
NCHomeSales <- rename(NCHomeSales, "2010" = "2010-05")
NCHomeSales <- rename(NCHomeSales, "2011" = "2011-05")
NCHomeSales <- rename(NCHomeSales, "2012" = "2012-05")
NCHomeSales <- rename(NCHomeSales, "2013" = "2013-05")
NCHomeSales <- rename(NCHomeSales, "2014" = "2014-05")
NCHomeSales <- rename(NCHomeSales, "2015" = "2015-05")
NCHomeSales <- rename(NCHomeSales, "2016" = "2016-05")
NCHomeSales <- rename(NCHomeSales, "2017" = "2017-05")
NCHomeSales <- rename(NCHomeSales, "2018" = "2018-05")

NCHomeSales <- pivot_longer(NCHomeSales,c("1996", "1997", "1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018"),names_to = 'YR',values_to = 'ZHVI')

NCHomeSales <- group_by(NCHomeSales, Metro)

ggplot(data=NCHomeSales, aes(x=Metro,y=ZHVI)) +
  geom_violin()+
  geom_boxplot(width=0.1) 
```

a. According to the results, which market has the lowest median price (represented as horizontal bar in box plot)?

Charlotte-Concord-Gastonia

b. The violin plot will show density meaning the wider the plot is, the more observations occur within
that area. Which market has the most density around the median value of homes?

Charlotte-Concord-Gastonia

### Relocation Home Value Comparison

```{r}
NationalHomeSales <- filter(Sales, State %in% c("IL", "TX", "CO", "NY") & RegionName %in% c("Chicago", "Denver", "Houston", "New York"))

NationalHomeSales <- select(NationalHomeSales, RegionName, State, Metro, "1996-05", "1997-05", "1998-05", "1999-05", "2000-05", "2001-05", "2002-05", "2003-05", "2004-05", "2005-05", "2006-05", "2007-05", "2008-05", "2009-05", "2010-05", "2011-05", "2012-05", "2013-05", "2014-05", "2015-05", "2016-05", "2017-05", "2018-05")

NationalHomeSales <- rename(NationalHomeSales, "1996" = "1996-05")
NationalHomeSales <- rename(NationalHomeSales, "1997" = "1997-05")
NationalHomeSales <- rename(NationalHomeSales, "1998" = "1998-05")
NationalHomeSales <- rename(NationalHomeSales, "1999" = "1999-05")
NationalHomeSales <- rename(NationalHomeSales, "2000" = "2000-05")
NationalHomeSales <- rename(NationalHomeSales, "2001" = "2001-05")
NationalHomeSales <- rename(NationalHomeSales, "2002" = "2002-05")
NationalHomeSales <- rename(NationalHomeSales, "2003" = "2003-05")
NationalHomeSales <- rename(NationalHomeSales, "2004" = "2004-05")
NationalHomeSales <- rename(NationalHomeSales, "2005" = "2005-05")
NationalHomeSales <- rename(NationalHomeSales, "2006" = "2006-05")
NationalHomeSales <- rename(NationalHomeSales, "2007" = "2007-05")
NationalHomeSales <- rename(NationalHomeSales, "2008" = "2008-05")
NationalHomeSales <- rename(NationalHomeSales, "2009" = "2009-05")
NationalHomeSales <- rename(NationalHomeSales, "2010" = "2010-05")
NationalHomeSales <- rename(NationalHomeSales, "2011" = "2011-05")
NationalHomeSales <- rename(NationalHomeSales, "2012" = "2012-05")
NationalHomeSales <- rename(NationalHomeSales, "2013" = "2013-05")
NationalHomeSales <- rename(NationalHomeSales, "2014" = "2014-05")
NationalHomeSales <- rename(NationalHomeSales, "2015" = "2015-05")
NationalHomeSales <- rename(NationalHomeSales, "2016" = "2016-05")
NationalHomeSales <- rename(NationalHomeSales, "2017" = "2017-05")
NationalHomeSales <- rename(NationalHomeSales, "2018" = "2018-05")

NationalHomeSales <- pivot_longer(NationalHomeSales,c("1996", "1997", "1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018"),names_to = 'YR',values_to = 'ZHVI')

NationalHomeSales <- group_by(NationalHomeSales, Metro)

ggplot(data=NationalHomeSales, aes(x=YR,y=ZHVI)) +
  geom_point() +
  facet_wrap(~Metro) +
  labs(x="Year", title="City Home Value Comparison")+
  theme(axis.text.x = element_text(angle = 90, vjust=0.5, size=5)) +
  scale_y_continuous(name="Home Values (in $)", labels = scales::comma) 
  
  


  
```

a. Based on your analysis, which city’s housing is most affordable?

Houston

   Least affordable?

New York

b. Which cities saw the largest change in prices over the past 5 years?

New York

   Which city has remained more consistent (i.e., no huge swings up or down in home values)?
   
Houston  
   
c. During the market downturn in 2012, which cities were most impacted?

Denver, New York

   Which cities have recovered?
   
Denver, New York
   
   
