---
output:
  word_document: default
  html_document: default
---
# Charlie Wilds
# BAN 502
# Module 3 Assignment 1

```{r}
library(tidyverse)
library(lubridate)
library(tidymodels)
```

```{r}
bike <- read_csv("bike_cleaned.csv")

bike = bike%>% mutate(dteday =mdy(dteday))
bike = bike%>% mutate(season =factor(season))
bike = bike%>% mutate(mnth =factor(mnth))
bike = bike%>% mutate(holiday =factor(holiday), weekday =factor(weekday))
bike = bike%>% mutate(workingday =factor(workingday), weathersit =factor(weathersit))
bike = bike%>% mutate(hr =factor(hr))
```

```{r}
# Task 1
set.seed(1234)
bike_split = initial_split(bike, prob = 0.70, strata = count)
train = training(bike_split)
test = testing(bike_split)
```

```{r}
# Task 2
nrow(train)
nrow(test)
```
The training set has a total of 13,036 rows. The testing set has 4,343.

```{r}
# Task 3
train_simp = recipe(count ~ season + mnth + hr + holiday + weekday + temp + weathersit, train)
train_simp

lm_model = 
  linear_reg() %>%
  set_engine("lm")

lm_wflow =
  workflow() %>%
  add_model(lm_model) %>%
  add_recipe(train_simp)

lm_fit = fit(lm_wflow, train)

confint(lm_fit$fit$fit$fit)

summary(lm_fit$fit$fit$fit)


```
This model showed many variables that had a very low p - value which is very encouraging. The model also had a healthy adjusted R-squared of 0.6229. Both of these are signs that this model includes multiple significant variables and could be very helpful as a whole.

```{r}
# Task 4
predict_train = lm_fit %>% predict(train) %>% bind_cols(train) %>% metrics(truth = count, estimate = .pred)
predict_train

ggplot(predict_train,aes(x=.estimate)) +
  geom_histogram() +
  theme_bw()

```

The histogram showed a pretty even split between the variables.

```{r}
# Task 5
test_simp = recipe(count ~ season + mnth + hr + holiday + weekday + temp + weathersit, test)
test_simp

test_model = 
  linear_reg() %>%
  set_engine("lm")

test_wflow =
  workflow() %>%
  add_model(test_model) %>%
  add_recipe(test_simp)

test_fit = fit(test_wflow, test)

confint(test_fit$fit$fit$fit)

summary(test_fit$fit$fit$fit)
```

The adjusted r-squared for the testing set is 0.623 which is very close to the r-squared of the training set which suggests that there is no overfitting.