---
output:
  word_document: default
  html_document: default
---
```{r}
# install.packages("gridExtra")
# install.packages("vip")
# install.packages("ranger")
```

```{r include = FALSE}
library(tidyverse)
library(tidymodels)
library(caret)
library(gridExtra)
library(vip)
library(ranger)
library(naniar)
```

```{r}
drug = read_csv("drug_data-1.csv")
```
```{r}
names(drug) = c("ID", "Age", "Gender", "Education", "Country", "Ethnicity","Nscore", "Escore", "Oscore", "Ascore", "Cscore", "Impulsive","SS", "Alcohol", "Amphet", "Amyl", "Benzos", "Caff", "Cannabis","Choc", "Coke", "Crack", "Ecstasy", "Heroin", "Ketamine", "Legalh","LSD", "Meth", "Mushrooms", "Nicotine", "Semer", "VSA")

# str(drug)
```

```{r}
drug[drug == "CL0"] = "No"
drug[drug == "CL1"] = "No"
drug[drug == "CL2"] = "Yes"
drug[drug == "CL3"] = "Yes"
drug[drug == "CL4"] = "Yes"
drug[drug == "CL5"] = "Yes"
drug[drug == "CL6"] = "Yes"
```

```{r}
drug_clean = drug %>% mutate_at(vars(Age:Ethnicity), funs(as_factor)) %>%
  mutate(Age = factor(Age, labels = c("18_24", "25_34", "35_44",
                                      "45_54", "55_64", "65_"))) %>%
  mutate(Gender = factor(Gender, labels = c("Male", "Female"))) %>%
  mutate(Education = factor(Education, labels =
                              c("Under16", "At16", "At17", "At18", "SomeCollege",
                                "ProfessionalCert", "Bachelors", "Masters", "Doctorate"))) %>%
  mutate(Country = factor(Country,
                          labels = c("USA", "NewZealand", "Other", "Australia",
                                     "Ireland","Canada","UK"))) %>%
  mutate(Ethnicity = factor(Ethnicity,
                            labels = c("Black", "Asian", "White", "White/Black", "Other",
                                       "White/Asian", "Black/Asian"))) %>%
  mutate_at(vars(Alcohol:VSA), funs(as_factor)) %>%
  select(-ID)
```

```{r}
# str(drug_clean)
```

```{r}
drug_clean = drug_clean %>% select(!(Alcohol:Mushrooms)) %>% select(!(Semer:VSA))
names(drug_clean)
```

```{r}
# Task 1
vis_miss(drug_clean)
```
There is no missingness in this dataframe.

```{r}
# Task 2
set.seed(1234)
drug_split = initial_split(drug_clean, prob = 0.70, strata = Nicotine)
train = training(drug_split)
test = testing(drug_split)
```

```{r}
# Task 3 (1)
p1 = ggplot(train, aes(x = Age, fill = Nicotine)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = Gender, fill = Nicotine)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = Education, fill = Nicotine)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = Country, fill = Nicotine)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

```{r}
# Task 3(2)
p1 = ggplot(train, aes(x = Ethnicity, fill = Nicotine)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = Nscore, fill = Nicotine)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = Escore, fill = Nicotine)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = Oscore, fill = Nicotine)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

```{r}
# Task 3 (3)
p1 = ggplot(train, aes(x = Ascore, fill = Nicotine)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = Cscore, fill = Nicotine)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = Impulsive, fill = Nicotine)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = SS, fill = Nicotine)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

```{r}
# Task 4 (1)
set.seed(123)
drug_folds = vfold_cv(train, v = 5)
```

```{r}
# Task 4 (2)
drug_recipe = recipe(Nicotine ~., train) %>%
  step_dummy(all_nominal(), -all_outcomes())

rf_model = rand_forest(mtry = tune(), min_n = tune(), trees = 100) %>%
  set_engine("ranger", importance = "permutation") %>%
  set_mode("classification")

drug_wflow = 
  workflow() %>% 
  add_model(rf_model) %>% 
  add_recipe(drug_recipe)

set.seed(123)
rf_res = tune_grid(
  drug_wflow,
  resamples = drug_folds,
  grid = 20)
```

```{r}
# Task 4 (3)
rf_res %>%
  collect_metrics() %>%
  filter(.metric == "accuracy") %>%
  select(mean, min_n, mtry) %>%
  pivot_longer(min_n:mtry,
    values_to = "value",
    names_to = "parameter"
  ) %>%
  ggplot(aes(value, mean, color = parameter)) +
  geom_point(show.legend = FALSE) +
  facet_wrap(~parameter, scales = "free_x") +
  labs(x = NULL, y = "Accuracy")
```

```{r}
# Task 4 (4)
drug_recipe = recipe(Nicotine ~., train) %>%
  step_dummy(all_nominal(), -all_outcomes())

rf_model = rand_forest(mtry = tune(), min_n = tune(), trees = 100) %>%
  set_engine("ranger", importance = "permutation") %>%
  set_mode("classification")

drug_wflow = 
  workflow() %>% 
  add_model(rf_model) %>% 
  add_recipe(drug_recipe)

rf_grid = grid_regular(
  mtry(range = c(2, 8)),
  min_n(range = c(5, 20)),
  levels = 10)

set.seed(123)
rf_res_tuned = tune_grid(
  drug_wflow,
  resamples = drug_folds,
  grid = rf_grid)
```

```{r}
# Task 4 (5)
rf_res_tuned %>%
  collect_metrics() %>%
  filter(.metric == "accuracy") %>%
  select(mean, min_n, mtry) %>%
  pivot_longer(min_n:mtry,
    values_to = "value",
    names_to = "parameter"
  ) %>%
  ggplot(aes(value, mean, color = parameter)) +
  geom_point(show.legend = FALSE) +
  facet_wrap(~parameter, scales = "free_x") +
  labs(x = NULL, y = "Accuracy")
```


```{r}
# Task 5 (1)
best_rf = select_best(rf_res_tuned, "accuracy")

final_rf = finalize_workflow(
  drug_wflow,
  best_rf)

final_rf

final_rf_fit = fit(final_rf, train)
```
```{r}
# Task 5 (2)
final_rf_fit %>% pull_workflow_fit() %>% vip(geom = "point")
```

SS, Country_UK, and Oscore are the most important variables in the model.

```{r}
# Task 6 (Training Set)
trainpredrf = predict(final_rf_fit, train)
head(trainpredrf)

confusionMatrix(trainpredrf$.pred_class, train$Nicotine, 
                positive = "Yes")

```

```{r}
# Task 6 (Testing Set)
testpredrf = predict(final_rf_fit, test)
head(testpredrf)

confusionMatrix(testpredrf$.pred_class, test$Nicotine, 
                positive = "Yes")
```
The model performed performed much better on the training set. The accuracy, sensitivity, and specificity were all considerably higher. The p-value was also much lower for the training set.

Task 7

I think this model could be used in a real-world application. In fact, I think it can be used for something very similar to the data set we used for this assignment. Identifying trends and key points within drug use can be helpful when trying to fight substance abuse. The model could also be used in other medical areas. Specificity is one concern when using this model as it was mediocre when used with the training set and very low when used with the testing set. 
