---
output:
  word_document: default
  html_document: default
---
## Charlie Wilds
## BAN 502
## Module 2 Assignment 1


```{r}
# install.packages("tidymodels")
```

```{r}
# install.packages("GGally")
```
```{r}
# install.packages("lmtest")
```
```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)
```
```{r}
# Task 1
air = airquality
```

```{r}
# Task 2
str(air)
summary(air)
```

There are 6 variables and 153 observations in the "air" data set. There is missing data in multiple within multiple variables, and the most likely response variable is "Ozone".

```{r}
# Task 2
air2 = drop_na(air)
str(air2)
```
The "air2" data set contains 111 rows and 6 columns. The drop_na function deleted 42 rows.

```{r}
# Task 3
ggpairs(air2)
ggcorr(air2, label=TRUE)
```
"Temp" is most strongly correlated with "Ozone".
"Day" is least strongly correlated with "Ozone".

```{r}
# Task 4
ggplot(data=air2, aes(x=Temp, y=Ozone)) +
  geom_point()
```

There is a moderate positive correlation between Temp and Ozone.

```{r}
# Task 5 Part 1
air2_simp = recipe(Ozone ~ Temp, air2)
air2_simp
```
```{r}
# Task 5 Part 2
lm_model = 
  linear_reg() %>%
  set_engine("lm")
```

```{r}
# Task 5 Part 3
lm_wflow =
  workflow() %>%
  add_model(lm_model) %>%
  add_recipe(air2_simp)
```

```{r}
# Task 5 Part 4
lm_fit = fit(lm_wflow, air2)
```

```{r}
# Task 5 Part 5
confint(lm_fit$fit$fit$fit)
summary(lm_fit$fit$fit$fit)
```
The Temp variable was highly significant in predicting the Ozone variable, but there was a just a moderately high R-squared value (.4833) so this model is somewhat efficient but not super reliable.

```{r}
# Task 6
ggplot(data=air2, aes(x=Temp, y=Ozone)) +
  geom_point() +
  geom_smooth(method="lm", se = FALSE)

```

```{r}
testdata = data.frame(Temp = 80)
predict(lm_fit, new_data = testdata)
```
The prediction for the Ozone variable while the Temp variable = 80 is 47.48.

### Assumption 1
Our model shows that there is somewhat of a linear relationship between the Ozone and Temp variables, but, that there is a non-linear presence as well.

### Assumption 2
```{r}
dwtest(lm_fit$fit$fit$fit)
```
The p-value is greater than .05, which indicates that the residuals are most likely independent.

### Assumption 3
```{r}
air2 = air2 %>% mutate(resid1 = lm_fit$fit$fit$fit$residuals)
ggplot(air2,aes(x=Temp, y=resid1)) +
  geom_point() +
  theme_bw()
```

The plot shows that there is non-linear effect in our model.

### Assumption 4
```{r}
ggplot(air2,aes(x=resid1)) +
  geom_histogram() +
  theme_bw()
```

The histogram of our model's residuals is somewhat normal.