---
output:
  word_document: default
  html_document: default
---
```{r}
# install.packages("caret")
# install.packages("rpart")
# install.packages("rattle")
# install.packages("RColorBrewer")
```

```{r,include = FALSE}
library(tidyverse)
library(tidymodels)
library(caret)
library(rpart)
library(rpart.plot)
library(rattle)
library(RColorBrewer)
```

```{r}
parole<- read_csv("parole (1).csv")

parole = parole %>% mutate(male = as_factor(male)) %>%
  mutate(male = fct_recode(male, "male" = "1", "female" = "0"))
parole = parole %>% mutate(race = as_factor(race)) %>%
  mutate(race = fct_recode(race, "white" = "1", "other" = "2"))
parole = parole %>% mutate(state = as_factor(state)) %>%
  mutate(state = fct_recode(state, "other" = "1", "Kentucky" = "2", "Louisiana" = "3", "Virginia" = "4"))
parole = parole %>% mutate(crime = as_factor(crime)) %>%
  mutate(crime = fct_recode(crime, "other" = "1", "larceny" = "2", "drug-related" = "3", "driving-related" = "4"))
parole = parole %>% mutate(multiple.offenses = as_factor(multiple.offenses)) %>%
  mutate(multiple.offenses = fct_recode(multiple.offenses, "multiple" = "1", "not multiple" = "0"))
parole = parole %>% mutate(violator = as_factor(violator)) %>%
  mutate(violator = fct_recode(violator, "violated" = "1", "did not violate" = "0"))
```

```{r}
# Task 1
set.seed(12345)
parole_split = initial_split(parole, prob = 0.70, strata = violator)
train = training(parole_split)
test = testing(parole_split)
```

```{r}
# Task 2
class_recipe = recipe(violator ~ ., train) %>%
  step_dummy(all_nominal(), -all_outcomes())

class_model = decision_tree() %>% 
  set_engine("rpart", model = TRUE) %>%
  set_mode("classification")

class_wflow = 
  workflow() %>% 
  add_model(class_model) %>% 
  add_recipe(class_recipe)

class_fit = fit(class_wflow, train)

class_fit %>%
  pull_workflow_fit() %>%
  pluck("fit")

tree = class_fit %>% 
  pull_workflow_fit() %>% 
  pluck("fit")

fancyRpartPlot(tree, tweak=1.25)
```
Task 3

The parolee described in Task 3 would be classified as a non-violator. The beginning branch suggests that the parolee is not from Louisiana, so I chose no. The next branch suggests that the parolee did not have multiple offenses so I once again chose no. I then followed the max sentence is < 13, time served is not >= 5.1, and age is < 41 to arrive at a 44% chance of violation which would be classified as a non-violator. 

```{r}
# Task 4
class_fit$fit$fit$fit$cptable
```
The optimal CP value for this tree is 0.02542373. The tree from Task 2 is not associated with this cp value.

```{r}
# Task 5 (1)
set.seed(123)
folds = vfold_cv(train, v = 5)
```

```{r}
# Task 5 (2)
tuned_recipe = recipe(violator ~., train) %>%
  step_dummy(all_nominal(),-all_outcomes())

tuned_model = decision_tree(cost_complexity = tune()) %>% 
  set_engine("rpart", model = TRUE) %>%
  set_mode("classification")

tuned_grid = grid_regular(cost_complexity(),
                          levels = 25) 

tuned_wflow = 
  workflow() %>% 
  add_model(tuned_model) %>% 
  add_recipe(tuned_recipe)

tuned_res = 
  tuned_wflow %>% 
  tune_grid(
    resamples = folds,
    grid = tuned_grid
    )

tuned_res
```
```{r}
# Task 5
tuned_res %>%
  collect_metrics() %>%
  ggplot(aes(cost_complexity, mean)) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2)

best_tree = tuned_res %>%
  select_best("accuracy")

best_tree
```
Task 6

The cp value that yields the optimal accuracy value is 0.1.


```{r}
# Task 7 (1)
final_wf = 
  tuned_wflow %>% 
  finalize_workflow(best_tree)
```

```{r}
# Task 7 (2)
final_fit = fit(final_wf, train)

tree_2 = final_fit %>% 
  pull_workflow_fit() %>% 
  pluck("fit")

# fancyRpartPlot(tree_2, tweak=1.25)


```

```{r}
# Task 8
treepred = predict(final_fit, train, type = "class")
head(treepred)

confusionMatrix(treepred$.pred_class,train$violator)
```
The accuracy of the root generated in task 7 is .8836.

```{r}
# Task 9 (1)
blood <- read_csv("Blood.csv")

blood = blood %>% mutate(DonatedMarch = as_factor(DonatedMarch)) %>%
  mutate(DonatedMarch = fct_recode(DonatedMarch, "yes" = "1", "no" = "0"))
```
```{r}
# Task 9 (2)
set.seed(1234)
blood_split = initial_split(blood, prob = 0.70, strata = DonatedMarch)
train_2 = training(blood_split)
test_2 = testing(blood_split)
```

```{r}
# Task 9 (3)
set.seed(1234)
blood_folds = vfold_cv(train_2, v = 5)

blood_recipe = recipe(DonatedMarch ~., train_2) %>%
  step_dummy(all_nominal(),-all_outcomes())

blood_model = decision_tree(cost_complexity = tune()) %>% 
  set_engine("rpart", model = TRUE) %>%
  set_mode("classification")

blood_grid = grid_regular(cost_complexity(),
                          levels = 25) 

blood_wflow = 
  workflow() %>% 
  add_model(blood_model) %>% 
  add_recipe(blood_recipe)

blood_res = 
  blood_wflow %>% 
  tune_grid(
    resamples = blood_folds,
    grid = blood_grid
    )

blood_res

blood_res %>%
  collect_metrics() %>%
  ggplot(aes(cost_complexity, mean)) +
  geom_line(size = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2)

blood_tree = blood_res %>%
  select_best("accuracy")

blood_tree
```


```{r}
# Task 10
blood_final_wf = 
  blood_wflow %>% 
  finalize_workflow(blood_tree)

blood_final_fit = fit(blood_final_wf, train_2)

blood_tree_2 = blood_final_fit %>% 
  pull_workflow_fit() %>% 
  pluck("fit")

# fancyRpartPlot(blood_tree_2, tweak=1.25)
```

I was very confused by the instructions for tasks 9 and 10. I spent a couple hours trying to plot this final tree without an error but could not do it.

```{r}
# Task 11
treepred_2 = predict(blood_final_fit, train_2, type = "class")
head(treepred_2)

confusionMatrix(treepred_2$.pred_class,train_2$DonatedMarch)
```
The accuracy of the tree generated in task 10 is .7616.

